Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-02-24 analysis/paper/paper.Rmd
Further changes to intial wording in methods section
Added bookdown references in text. Temporarily turned a code change filtering out NA values in the results section into an in-line comment so the code will run for now, albeit with "NA" still in the legend of the biplot

# this block of code below shows one way to discretize cortex percentage
# into three groups. We need to explore other cutoffs, and other grouping
# variables besides dorsal cortex. This code below is a good template for
# starting these explorations

# Note, trying to fix NA by removing all rows which lack dorsal cortex values. Issue with the initial set of data with NA values being passed through PCA. In the process of fixing

ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
  filter(!is.na(dorsal_cortex_perc)) %>% 
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 60) ~ "Secondary",
             between(dorsal_cortex_perc, 61, 100) ~ "Primary"
           ))

@@

  The PCA biplot above shows flake shape (as defined within the first two primary dimensions) in relation to dorsal cortex class. The primary class of dorsal cortex, representing initial, unretouched flakes in the reduction sequence, has the smallest range of shape variation. Secondary flakes, which have been retouched and thus have less dorsal cortex than the primary flakes, show a slighly larger range of shape variation. Lastly, the heavily worked tertiary flakes at the end of the reduction sequence show the greatest amount of shape variation.

>>>>

# this block of code below shows one way to discretize cortex percentage
# into three groups. We need to explore other cutoffs, and other grouping
# variables besides dorsal cortex. This code below is a good template for
# starting these explorations
```

```{r cortex-biplot}
# Note, trying to fix NA by removing all rows which lack dorsal cortex values. Issue with the initial set of data with NA values being passed through PCA. In the process of fixing

ma_flakes_tr_with_groups <-
  ma_flakes_tr %>%
 # filter(!is.na(dorsal_cortex_perc)) %>% 
  slice(-outlier_ids) %>%
  mutate(dorsal_cortext_group =
           case_when(
             between(dorsal_cortex_perc, 0, 0) ~ "Tertiary",
             between(dorsal_cortex_perc, 1, 60) ~ "Secondary",
             between(dorsal_cortex_perc, 61, 100) ~ "Primary"
           ))

@@

<!--“biplot above” replace this figure \@ref(fig:code-block-name)  code-block-name is like this ```{r code-block-name} be sure to give them descriptive, simple names -->

  Figure \@ref(fig:cortex-biplot) shows flake shape (as defined within the first two primary dimensions) in relation to dorsal cortex class. The primary class of dorsal cortex, representing initial, unretouched flakes in the reduction sequence, has the smallest range of shape variation. Secondary flakes, which have been retouched and thus have less dorsal cortex than the primary flakes, show a slighly larger range of shape variation. Lastly, the tertiary flakes at the end of the reduction sequence show the greatest amount of shape variation.
